---
title: 'Reward Network GluCEST and RR Statistics: HMRS VOI Analyses'
author: "Valerie Jill Sydnor"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: yes
    toc_depth: '5'
theme: cerulean
geometry: margin=1.9cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/")
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=65),tidy=TRUE)
library(dplyr)
library(knitr)
library(kableExtra)
library(ppcor)
```

\newpage

```{r include=FALSE}
#read in sample demographics and clinical measures
glucest <- read.csv("./GLUCEST-Clinical-Demographics-Measures-N45.csv", header=TRUE) #csv created by Prepare_Demographics_ClinicalMeasures_Data.Rmd
```

```{r include=FALSE}
#read in HMRS VOI Volume and Coverage measures
VOI.Coverage.MP2RAGEspace <- read.csv("./OutputMeasures/SVSROI-Coverage-MP2RAGEspace.csv", sep='\t', header=TRUE) #original volume of the VOI in MP2RAGE space and reward network/non-reward cortex VOI percent coverage
VOI.Coverage.CESTspace <- read.csv("./OutputMeasures/SVSROI-Coverage-CESTspace.csv", sep='\t', header=TRUE) #volume of the VOI present in the CEST FOV, and reward network/non-reward cortex VOI coverage in CEST space

#read in HMRS VOI GluCEST measures
VOI.GluCEST <- read.csv("./OutputMeasures/GluCEST-SVSROI-Measures.csv", sep='\t', header=TRUE) #mean GluCEST in the SVS VOI
VOI.Reward.GluCEST <- read.csv("./OutputMeasures/GluCEST-SVSROI-RewardNetwork-Measures.csv", sep='\t', header=TRUE) #mean GluCEST in the reward network portion of the SVS VOI
VOI.NonReward.GluCEST <- read.csv("./OutputMeasures/GluCEST-SVSROI-NonReward-Measures.csv", sep='\t', header=TRUE) #mean GluCEST in the non-reward portion of the SVS VOI
```

```{r include=FALSE}
#combine VOI Volume/Coverage and GluCEST measures
VOI.GluCEST <- cbind(VOI.Coverage.MP2RAGEspace, VOI.Coverage.CESTspace, VOI.GluCEST, VOI.Reward.GluCEST, VOI.NonReward.GluCEST)
VOI.GluCEST <- VOI.GluCEST[-5] #remove duplicate column for "Case"
VOI.GluCEST <- VOI.GluCEST %>% dplyr::select(-Subject) #remove duplicate columns for "Subject"
```

```{r warning=FALSE, include=FALSE}
#read in HMRS VOI Absolute Concentration measures

#Identify GluCEST study sample cases that have 1HMRS data (N=25)
setwd("~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/sydnor_glucest_rewardresponsiveness_2020/R_Statistics/")
system("./extract_sample_HMRSMeasures.sh", wait=TRUE) #bash script

VOI.MRS <- read.csv("../../MRSMeasures/GluCEST-HMRS-ACC-VoxelData_Timept1_PassQC.csv", header=TRUE) #HMRS concentration measures
VOI.MRS <- VOI.MRS %>% dplyr::rename("Case" = "ID")
```

\newpage 

# Identify Final HMRS Sample Based on the Percent of HRMS VOI included in the GluCEST FOV

**Calculate percent of the HMRS VOI included in the GluCEST FOV**
```{r}
VOI.GluCEST <- VOI.GluCEST %>% mutate(VOI.FOV.Overlap=((SVSROI_Volume_CESTspace/SVSROI_Total_MP2RAGEspace)*100))
FOVcoverage <- data.frame(VOI.GluCEST$Case, VOI.GluCEST$VOI.FOV.Overlap)
FOVcoverage %>% arrange(VOI.GluCEST.VOI.FOV.Overlap)
```
**Remove 5 participants with < 20% of the HMRS VOI included in the GluCEST FOV**
```{r}
VOI.MRS.GluCEST <- merge(glucest, VOI.MRS, by = "Case")
VOI.MRS.GluCEST <- merge(VOI.MRS.GluCEST, VOI.GluCEST, by = "Case")
VOI.MRS.GluCEST <- VOI.MRS.GluCEST %>% filter(VOI.FOV.Overlap > 20) #remove participants with very low overlap between the HMRS VOI and the GluCEST FOV to enable appropriate methodological comparison
```

**Examine HMRS VOI Coverage Characteristics**

*Number of participants with > 20% of the HMRS VOI included in the GluCEST FOV*
```{r}
nrow(VOI.MRS.GluCEST)
```

*Participant Diagnostic Groups*
```{r}
table(VOI.MRS.GluCEST$Control_Coded)
table(VOI.MRS.GluCEST$Diagnosis_NC_MDD_Pro_Schiz_Coded)
```

*Mean (SD) Percent of HMRS VOI included in the GluCEST FOV*
```{r}
mean(VOI.MRS.GluCEST$VOI.FOV.Overlap)
sd(VOI.MRS.GluCEST$VOI.FOV.Overlap)
```

*Mean (SD) Percent of the HMRS VOI that falls within the Reward Network*
```{r}
mean(VOI.MRS.GluCEST$RewardNetwork_Percent_MP2RAGEspace)
sd(VOI.MRS.GluCEST$RewardNetwork_Percent_MP2RAGEspace)
```

*Mean (SD) Percent of the SVS VOI that falls within Non-Reward Cortex*
```{r}
mean(VOI.MRS.GluCEST$NonReward_Percent_MP2RAGEspace)
sd(VOI.MRS.GluCEST$NonReward_Percent_MP2RAGEspace)
```

\newpage 

# Associations Between BAS RR Scores and Dual Method Anterior Cingulate Glutamate

## HMRS

### HMRS Glutamate Concentration and BAS RR

**Multiple Linear Regression**
```{r}
#linear regression between HMRS Glutamate and RR controlling for age, sex, and fCSF
summary(lm(VOI.MRS.GluCEST$BAS_Reward_totalscore ~ VOI.MRS.GluCEST$Conc.Glu + VOI.MRS.GluCEST$age_scan + VOI.MRS.GluCEST$sex + VOI.MRS.GluCEST$fCSF))
```

**Partial R**
```{r}
covariates <- data.frame(VOI.MRS.GluCEST$age_scan, VOI.MRS.GluCEST$sex, VOI.MRS.GluCEST$fCSF)
pcor.test(VOI.MRS.GluCEST$Conc.Glu, VOI.MRS.GluCEST$BAS_Reward_totalscore, covariates)$estimate
```


\newpage

## GluCEST

### HMRS VOI GluCEST and BAS RR

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST in the HMRS VOI and RR controlling for age and sex
summary(lm(VOI.MRS.GluCEST$BAS_Reward_totalscore ~ VOI.MRS.GluCEST$SVSROI_CEST_mean + VOI.MRS.GluCEST$age_scan + VOI.MRS.GluCEST$sex))
```

**Partial R**
```{r}
covariates <- data.frame(VOI.MRS.GluCEST$age_scan, VOI.MRS.GluCEST$sex)
pcor.test(VOI.MRS.GluCEST$SVSROI_CEST_mean, VOI.MRS.GluCEST$BAS_Reward_totalscore, covariates)$estimate
```

### HMRS VOI Reward Network GluCEST and BAS RR

**Partial R**
```{r}
covariates <- data.frame(VOI.MRS.GluCEST$age_scan, VOI.MRS.GluCEST$sex)
pcor.test(VOI.MRS.GluCEST$SVSROI_Reward_CEST_mean, VOI.MRS.GluCEST$BAS_Reward_totalscore, covariates)$estimate
```

### HMRS VOI Non-Reward GluCEST and BAS RR

**Partial R**
```{r}
covariates <- data.frame(VOI.MRS.GluCEST$age_scan, VOI.MRS.GluCEST$sex)
pcor.test(VOI.MRS.GluCEST$SVSROI_NonReward_CEST_mean, VOI.MRS.GluCEST$BAS_Reward_totalscore, covariates)$estimate
```

\newpage

# GluCEST- and 1HMRS-derived Measures of Brain Glutamate are Positively Correlated 

## HMRS Glutamate and GluCEST

*Full sample*
```{r}
pcor.test(VOI.MRS.GluCEST$Conc.Glu, VOI.MRS.GluCEST$SVSROI_CEST_mean, VOI.MRS.GluCEST$fCSF) 
Glu.R <- pcor.test(VOI.MRS.GluCEST$Conc.Glu, VOI.MRS.GluCEST$SVSROI_CEST_mean, VOI.MRS.GluCEST$fCSF)$estimate
```

*Participants with > 50% of the HMRS VOI included in the GluCEST FOV*
```{r}
cordata <- VOI.MRS.GluCEST %>% dplyr::select(Conc.Glu,SVSROI_CEST_mean,VOI.FOV.Overlap,fCSF)
cordata <- cordata %>% filter(VOI.FOV.Overlap > 50)
pcor.test(cordata$Conc.Glu, cordata$SVSROI_CEST_mean, cordata$fCSF)
```

*Participants with > 90% of the SVS VOI included in the GluCEST FOV*
```{r}
cordata <- cordata %>% filter(VOI.FOV.Overlap > 90)
pcor.test(cordata$Conc.Glu, cordata$SVSROI_CEST_mean, cordata$fCSF)
```


## HMRS NAA and GluCEST

*Full sample*
```{r}
pcor.test(VOI.MRS.GluCEST$Conc.NAA, VOI.MRS.GluCEST$SVSROI_CEST_mean,  VOI.MRS.GluCEST$fCSF)
NAA.R <- pcor.test(VOI.MRS.GluCEST$Conc.NAA, VOI.MRS.GluCEST$SVSROI_CEST_mean,  VOI.MRS.GluCEST$fCSF)$estimate
```

## HMRS GSH and GluCEST

*Full sample*
```{r}
GSHdata <- VOI.MRS.GluCEST %>% dplyr::select(Conc.GSH , SVSROI_CEST_mean, VOI.FOV.Overlap, fCSF)
GSHdata <- na.omit(GSHdata) # N=17 due to CRLB QC
pcor.test(GSHdata$Conc.GSH, GSHdata$SVSROI_CEST_mean, GSHdata$fCSF)
GSH.R <- pcor.test(GSHdata$Conc.GSH, GSHdata$SVSROI_CEST_mean, GSHdata$fCSF)$estimate
```


## HMRS Cr/Pcr and GluCEST

*Full sample*
```{r}
pcor.test(VOI.MRS.GluCEST$Conc.Cr.PCr, VOI.MRS.GluCEST$SVSROI_CEST_mean, VOI.MRS.GluCEST$fCSF)
CrPCr.R <- pcor.test(VOI.MRS.GluCEST$Conc.Cr.PCr, VOI.MRS.GluCEST$SVSROI_CEST_mean, VOI.MRS.GluCEST$fCSF)$estimate
```

\newpage 

## Table of Correlation R Values
```{r}
Corrtable <- data.frame(Metabolite=character(), R.value=double())
Corrtable <- Corrtable %>% add_row(Metabolite="Glutamate", R.value = Glu.R )
Corrtable <- Corrtable %>% add_row(Metabolite="NAA", R.value = NAA.R)
Corrtable <- Corrtable %>% add_row(Metabolite="GSH", R.value = GSH.R )
Corrtable <- Corrtable %>% add_row(Metabolite="CrPCr", R.value = CrPCr.R)

Corrtable %>%
  arrange(desc(R.value)) %>%
  kable() %>%
  kable_styling()
```

