---
title: 'Reward Network GluCEST and RR Statistics: Reward Network Analyses'
author: "Valerie Jill Sydnor"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: yes
    toc_depth: '5'
theme: cerulean
geometry: margin=1.9cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/OutputMeasures/")
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=65),tidy=TRUE)
library(plyr)
library(dplyr)
library(knitr)
library(reader)
library(kableExtra)
library(ggplot2)
library(ppcor)
```

\newpage

```{r include=FALSE}
#read in sample demographics and clinical measures
glucest <- read.csv("../GLUCEST-Clinical-Demographics-Measures-N45.csv", header=TRUE) #csv created by Prepare_Demographics_ClinicalMeasures_Data.Rmd
```

```{r include=FALSE}
#Read in GluCEST % Contrast Measures, GM Density Measures, and Reward Network Coverage Measures

#list all .csv files in root directory
files <- list.files(getwd(), pattern='.csv', ignore.case=T, full.names = F) 

filenames <- c()
#generate variable names to assign file data to 
for(name in files){
  #remove "-Measures.csv"" from end of filename
  Rname <- gsub('.{13}$', '', name)
  #replace - with _ for R compatibility 
  Rname <- chartr(old = "-", new = "_", Rname) 
  #save filenames into a character vector 
  filenames <- append(filenames, Rname) 
}

#read in files and assign to variables
for(i in 1:18){
  #save filename as an individual string
  Rfilename <- sprintf("%s",filenames[i]) 
  #read in csv data for each file
  x <- read.csv(files[i], header=TRUE, sep='\t') 
  #assign csv data to Rfilename string 
  assign(Rfilename, x) 
}
rm(x)
```

\newpage

# Reward Network GluCEST v. Non-Reward GluCEST and RR 

**Multiple Linear Regression**
```{r}
#linear regression with age, sex, Reward Network GluCEST and Non-Reward GluCEST predicting BAS RR
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork$RewardNetwork_CEST_mean + GluCEST_NonReward$NonReward_CEST_mean + glucest$age_scan + glucest$sex))
```

**Reward Network Partial R**
```{r}
covariates <- data.frame(GluCEST_NonReward$NonReward_CEST_mean, glucest$age_scan, glucest$sex)
pcor.test(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork$RewardNetwork_CEST_mean, covariates)$estimate
```

**Non-Reward Network Partial R**
```{r}
covariates <- data.frame(GluCEST_RewardNetwork$RewardNetwork_CEST_mean, glucest$age_scan, glucest$sex)
pcor.test(glucest$BAS_Reward_totalscore, GluCEST_NonReward$NonReward_CEST_mean, covariates)$estimate
```

**Reward Network Association Plot (Figure 2)**
```{r echo=TRUE}
plotdata <- data.frame(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork$RewardNetwork_CEST_mean, glucest$Diagnosis_NC_MDD_Psy_Coded)

jpeg("~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/Figures/Images/BASRR_RewardNetworkTotal_CorrelationPlot_ColoredbyGroup.jpg", units="in", width=7.3, height=6.6, res=800)

ggplot(plotdata, aes(x=glucest.BAS_Reward_totalscore, y=GluCEST_RewardNetwork.RewardNetwork_CEST_mean, fill=as.factor(glucest.Diagnosis_NC_MDD_Psy_Coded))) +
  geom_point(color = "black", shape=21, size=3) +
  labs(x="\nBAS Reward Responsiveness Score\n", y="\nGluCEST % Contrast\n") +
  ggtitle("\n") +
  geom_smooth(method='lm', se=TRUE, fill=alpha(c("#ad0000"),.2), col="black") +
  theme(legend.title=element_blank()) +
  scale_y_continuous(breaks=c(6.5,7,7.5,8,8.5,9)) +
  scale_fill_manual(values=c(rgb(116,3,5,maxColorValue=255,alpha=255),
                             rgb(239,162,164,maxColorValue=255, alpha=255),
                             rgb(196,36,40,maxColorValue=255, alpha=255)),
                             labels=c("TD","DEP","PSY")) +
  theme(
    axis.title.x=element_text(family="Arial", vjust=0.5, size=17),
    axis.title.y=element_text(family="Arial",  size=17),
    axis.line = element_line(colour = "black"),
    axis.text=element_text(family="Arial",size=18),
    panel.background=element_blank(),
    axis.text.x = element_text(color="black"),
    axis.text.y = element_text(color="black"),
    legend.title=element_blank(), 
    legend.text=element_text(size=14, family="Arial"),
    legend.key = element_rect(fill = NA, colour = NA),
    legend.position="top", 
    legend.justification="left",
    legend.direction="horizontal")
```

**Reward Network GluCEST Between Typically Developing and Clinical Groups**
```{r}
summary(aov(GluCEST_RewardNetwork$RewardNetwork_CEST_mean ~ glucest$age_scan + glucest$sex + as.factor(glucest$Control_Coded)))
```

**Reward Network GluCEST and RR Association in Males v. Females (Interaction Effect for Sex)**
```{r}
#linear regression between GluCEST and RR controlling for age and including an interaction effect for sex
data <- data.frame(glucest$BAS_Reward_totalscore, glucest$age_scan, glucest$sex, GluCEST_RewardNetwork$RewardNetwork_CEST_mean)
data$glucest.sex <- as.factor(data$glucest.sex)
contrasts(data$glucest.sex) <- c(-.5,.5)
summary(lm(glucest.BAS_Reward_totalscore ~ (GluCEST_RewardNetwork.RewardNetwork_CEST_mean)*(glucest.sex) + glucest.age_scan, data=data))
```

\newpage

# Reward Network Anatomical Subdivision: Cortical and Subcortical GluCEST and RR

## Cortical Reward Network

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST and RR controlling for age and sex
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_Cortical$RewardNetwork_Cortical_CEST_mean + glucest$age_scan + glucest$sex))
```

**Partial R**
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex)
pcor.test(GluCEST_RewardNetwork_Cortical$RewardNetwork_Cortical_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

## Subcortical Reward Network

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST and RR controlling for age and sex
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_Subcortical$RewardNetwork_Subcortical_CEST_mean + glucest$age_scan + glucest$sex))
```

**Partial R**
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex)
pcor.test(GluCEST_RewardNetwork_Subcortical$RewardNetwork_Subcortical_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

**Subcortical Reward Network Association Plot (Figure 3)**
```{r}
plotdata <- data.frame(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork_Subcortical$RewardNetwork_Subcortical_CEST_mean, glucest$Diagnosis_NC_MDD_Psy_Coded)
decimalscale <- function(x) sprintf("%.1f", x)

jpeg("~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/Figures/Images/BASRR_RewardNetworkSubcortical_CorrelationPlot_ColoredbyGroup.jpg", units="in", width=7.3, height=6.6, res=800)

ggplot(plotdata, aes(x=glucest.BAS_Reward_totalscore, y=GluCEST_RewardNetwork_Subcortical.RewardNetwork_Subcortical_CEST_mean, fill=as.factor(glucest.Diagnosis_NC_MDD_Psy_Coded))) +
  geom_point(color = "black", shape=21, size=3) +
  labs(x="\nBAS Reward Responsiveness Score\n", y="\nGluCEST % Contrast\n") +
  ggtitle("\n") +
  geom_smooth(method='lm', se=TRUE, fill=alpha(c("gold"),.7), col="black") +
  theme(legend.title=element_blank()) +
  scale_y_continuous(breaks=c(6.0,7.0,8.0,9.0, 10.0, 11.0), labels=decimalscale) +
  scale_fill_manual(values=c(rgb(250,230,202,maxColorValue=255, alpha=255),
                             rgb(230,204,237,maxColorValue=255,alpha=255),
                             rgb(255,224,74,maxColorValue=255, alpha=255)),
                    labels=c("TD","DEP","PSY")) +
  theme(
    axis.title.x=element_text(family="Arial", vjust=0.5, size=17),
    axis.title.y=element_text(family="Arial",  size=17),
    axis.line = element_line(colour = "black"),
    axis.text=element_text(family="Arial",size=18),
    panel.background=element_blank(),
    axis.text.x = element_text(color="black"),
    axis.text.y = element_text(color="black"),
    legend.title=element_blank(), 
    legend.text=element_text(size=14, family="Arial"),
    legend.key = element_rect(fill = NA, colour = NA),
    legend.position="top", 
    legend.justification="left",
    legend.direction="horizontal")
```

### FDR correction 
```{r echo=TRUE}
ps <- c("0.1439989", "0.01326643") #p-values from multiple regressions
fdr.ps <- p.adjust(ps, method="fdr")
```

*Cortical Reward*
```{r}
fdr.ps[1]
```

*Subcortical Reward*
```{r}
fdr.ps[2]
```

\newpage

# Reward Network Valence Subdivision: Appetitive, Aversive, and Salience GluCEST and RR 

## Reward Network Appetitive Component

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST and RR controlling for age and sex
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_PositiveOnly$RewardNetwork_Positive_CEST_mean + glucest$age_scan + glucest$sex))
```

**Partial R**
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex)
pcor.test(GluCEST_RewardNetwork_PositiveOnly$RewardNetwork_Positive_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

## Reward Network Aversive Component

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST and RR controlling for age and sex
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_NegativeOnly$RewardNetwork_Negative_CEST_mean  + glucest$age_scan + glucest$sex))
```

**Partial R**
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex)
pcor.test(GluCEST_RewardNetwork_NegativeOnly$RewardNetwork_Negative_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

## Reward Network Salience Component

**Multiple Linear Regression**
```{r}
#linear regression between GluCEST and RR controlling for age and sex
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_Salience$RewardNetworkC_CEST_mean + glucest$age_scan + glucest$sex))
```

**Partial R**
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex)
pcor.test(GluCEST_RewardNetwork_Salience$RewardNetworkC_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

**Partial R Plot (Figure 4)**
```{r}
valence.analysis.results <- data.frame(Mask=character(), PartialR=double())
valence.analysis.results <- valence.analysis.results %>% add_row(Mask= "Reward Network", PartialR= 0.31)
valence.analysis.results <- valence.analysis.results %>% add_row(Mask= "Reward: Appetitive", PartialR= 0.29)
valence.analysis.results <- valence.analysis.results %>% add_row(Mask= "Reward: Aversive", PartialR= 0.23)
valence.analysis.results <- valence.analysis.results %>% add_row(Mask= "Reward: Salience", PartialR= 0.42)
valence.analysis.results <- valence.analysis.results %>% add_row(Mask= "Non Reward", PartialR= 0.03)

jpeg("/Users/valeriejill/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/Figures/Images/BASRR_RewardNetworkTotal_Valence_PartialR.jpg", units="in", width=7.3, height=6.6, res=800)

ggplot(data=valence.analysis.results, aes(x=Mask, y=PartialR, fill=Mask)) + geom_col() + 
  labs(x="") +
  labs(y="\nPartial R") +
  ggtitle("\n") +
  theme_minimal()+
  theme(
  axis.title.x=element_text(family="Arial", vjust=0.5, size=12),
  axis.title.y=element_text(family="Arial",  size=15),
  axis.line = element_line(colour = "black"),
  axis.text.y.left = element_text(family="Arial", size=18),
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  panel.grid.major.y = element_line(colour = "gray90"),
  panel.grid.major.x = element_line(colour = "white"),
  legend.position = "none") +
  scale_fill_manual(values=c("#710002", "#3a0807", "#3a0807","#3a0807","#09003b"))
  scale_y_continuous(limits = c(0,0.45), breaks=c(0,0.1,0.2,0.3,0.4)) 
```

### FDR correction
```{r echo=TRUE}
ps <- c("0.05553093","0.1337805","0.004709815") #p-values from multiple regressions
fdr.ps <- p.adjust(ps, method="fdr")
```

*Reward Appetitive Component*
```{r}
fdr.ps[1]
```

*Reward Aversive Component*
```{r}
fdr.ps[2]
```

*Reward Salience Component*
```{r}
fdr.ps[3]
```

\newpage 

# Sensitivity Analyses

**Gray Matter Density**

* Multiple Linear Regression
```{r}
#linear regression between GluCEST and RR controlling for age and sex and GM density
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork$RewardNetwork_CEST_mean + glucest$age_scan + glucest$sex + GMDensity_RewardNetwork$RewardNetwork_GMDensity_mean))
```

* Partial R
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex, GMDensity_RewardNetwork$RewardNetwork_GMDensity_mean)
pcor.test(GluCEST_RewardNetwork$RewardNetwork_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

**Reward Network Percent Coverage**

* Multiple Linear Regression
```{r}
#linear regression between GluCEST and RR controlling for age and sex and network percent coverage
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork$RewardNetwork_CEST_mean + glucest$age_scan + glucest$sex + RewardNetwork_PercentCoverage$RewardNetwork_PercentCoverage))
```

* Partial R
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex, RewardNetwork_PercentCoverage$RewardNetwork_PercentCoverage)
pcor.test(GluCEST_RewardNetwork$RewardNetwork_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

**Heatmap Analysis**

* Multiple Linear Regression
```{r}
#linear regression between GluCEST in 50% overlap voxels and RR controlling for age and sex 
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork_Heatmap50$RewardNetwork_50_CEST_mean + glucest$age_scan + glucest$sex))
```

* Partial R
```{r}
heatmap.data <- data.frame(GluCEST_RewardNetwork_Heatmap50$RewardNetwork_50_CEST_mean, glucest$BAS_Reward_totalscore, glucest$age_scan, glucest$sex)
heatmap.data <- heatmap.data %>% filter(GluCEST_RewardNetwork_Heatmap50.RewardNetwork_50_CEST_mean != "NA") #remove one case with no 50% overlap voxels
covariates <- data.frame(heatmap.data$glucest.age_scan, heatmap.data$glucest.sex)
pcor.test(heatmap.data$GluCEST_RewardNetwork_Heatmap50.RewardNetwork_50_CEST_mean, heatmap.data$glucest.BAS_Reward_totalscore, covariates)$estimate
```

**Group**

* Multiple Linear Regression
```{r}
#linear regression between GluCEST and RR controlling for age and sex and typically developing versus clinical group
summary(lm(glucest$BAS_Reward_totalscore ~ GluCEST_RewardNetwork$RewardNetwork_CEST_mean + glucest$age_scan + glucest$sex + glucest$Control_Coded))
```

* Partial R
```{r}
covariates <- data.frame(glucest$age_scan, glucest$sex, glucest$Control_Coded)
pcor.test(GluCEST_RewardNetwork$RewardNetwork_CEST_mean, glucest$BAS_Reward_totalscore, covariates)$estimate
```

# Specificity Analyses

**PRIME Scores**
```{r}
#linear regression between GluCEST and PRIME scores controlling for BAS Reward Responsiveness, age, and sex
summary(lm(GluCEST_RewardNetwork$RewardNetwork_CEST_mean ~ glucest$Prime_totalscore + glucest$BAS_Reward_totalscore + glucest$age_scan + glucest$sex))
```

**PROMIS Scores**
```{r}
#linear regression between GluCEST and PROMIS scores controlling for BAS Reward Responsiveness, age, and sex
summary(lm(GluCEST_RewardNetwork$RewardNetwork_CEST_mean ~ glucest$PROMIS_totalscore + glucest$BAS_Reward_totalscore + glucest$age_scan + glucest$sex))
```

**BAS Drive Scores**
```{r}
#linear regression between GluCEST and BAS Drive scores controlling for BAS Reward Responsiveness, age, and sex
summary(lm(GluCEST_RewardNetwork$RewardNetwork_CEST_mean ~ glucest$BAS_Drive_totalscore + glucest$BAS_Reward_totalscore + glucest$age_scan + glucest$sex))
```

**BAS Fun Scores**
```{r}
#linear regression between GluCEST and BAS Fun scores controlling for BAS Reward Responsiveness, age, and sex
summary(lm(GluCEST_RewardNetwork$RewardNetwork_CEST_mean ~ glucest$BAS_Fun_totalscore + glucest$BAS_Reward_totalscore + glucest$age_scan + glucest$sex))
```

\newpage

# Adjustment for Medication

```{r}
medications <- read.csv("../Medications/GluCEST_Medications_Timept1_PassQC.csv", header=TRUE) #read in patient medication data

#partial correlation between Reward Network GluCEST and RR controlling for psychotropic medication use (yes/no)
pcor.test(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork$RewardNetwork_CEST_mean, medications$Medication_history)

#partial correlation between Subcortical Reward Network GluCEST and RR controlling for psychotropic medication use (yes/no)
pcor.test(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork_Subcortical$RewardNetwork_Subcortical_CEST_mean, medications$Medication_history)

#partial correlation between Salience Reward Network GluCEST and RR controlling for psychotropic medication use (yes/no)
pcor.test(glucest$BAS_Reward_totalscore, GluCEST_RewardNetwork_Salience$RewardNetworkC_CEST_mean, medications$Medication_history)
```

# Reward Network by Anatomical Region: Harvard Oxford Region GluCEST and RR 

## Harvard Oxford Reward Network: Cortical Regions

**Filter data for reward network cortical regions, using > 50 mm^3 as region volume threshold for inclusion in analysis**
```{r echo=FALSE}
#get data for the 7 Harvard Oxford cortical regions reliably present in the GluCEST reward network, and filter out cases that do not meet the minimum coverage requirement ( > 50 mm^3 for each region)

frontal.pole <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Frontal_Pole_mean, GluCEST_HarvardOxford_Cortical_Reward$Frontal_Pole_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
frontal.pole <- filter(frontal.pole, GluCEST_HarvardOxford_Cortical_Reward.Frontal_Pole_numvoxels > 10 )

superior.frontal <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$SFG_mean, GluCEST_HarvardOxford_Cortical_Reward$SFG_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
superior.frontal <- filter(superior.frontal, GluCEST_HarvardOxford_Cortical_Reward.SFG_numvoxels > 10)

frontal.medial <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Frontal_Medial_Cortex_mean,  GluCEST_HarvardOxford_Cortical_Reward$Frontal_Medial_Cortex_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
frontal.medial <- filter(frontal.medial, GluCEST_HarvardOxford_Cortical_Reward.Frontal_Medial_Cortex_numvoxels > 10 )

subcallosal.cortex <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Subcallosal_Cortex_mean,  GluCEST_HarvardOxford_Cortical_Reward$Subcallosal_Cortex_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
subcallosal.cortex <- filter(subcallosal.cortex, GluCEST_HarvardOxford_Cortical_Reward.Subcallosal_Cortex_numvoxels > 10 )

paracingulate <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Paracingulate_Gyrus_mean,  GluCEST_HarvardOxford_Cortical_Reward$Paracingulate_Gyrus_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
paracingulate <- filter(paracingulate, GluCEST_HarvardOxford_Cortical_Reward.Paracingulate_Gyrus_numvoxels > 10 )

anterior.cingulate <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Anterior_cingulate_mean, GluCEST_HarvardOxford_Cortical_Reward$Anterior_cingulate_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
anterior.cingulate <- filter(anterior.cingulate, GluCEST_HarvardOxford_Cortical_Reward.Anterior_cingulate_numvoxels > 10 )

posterior.cingulate <- data.frame(GluCEST_HarvardOxford_Cortical_Reward$Posterior_cingulate_mean,  GluCEST_HarvardOxford_Cortical_Reward$Posterior_cingulate_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
posterior.cingulate <- filter(posterior.cingulate, GluCEST_HarvardOxford_Cortical_Reward.Posterior_cingulate_numvoxels > 10 )
```

**Frontal Pole**
```{r echo=FALSE}
covariates <- data.frame(frontal.pole$glucest.sex, frontal.pole$glucest.age_scan)
pcor.test(frontal.pole$GluCEST_HarvardOxford_Cortical_Reward.Frontal_Pole_mean, frontal.pole$glucest.BAS_Reward_totalscore, covariates)
```

**SFG**
```{r echo=FALSE}
covariates <- data.frame(superior.frontal$glucest.sex, superior.frontal$glucest.age_scan)
pcor.test(superior.frontal$GluCEST_HarvardOxford_Cortical_Reward.SFG_mean, superior.frontal$glucest.BAS_Reward_totalscore, covariates)
```

**Frontal Medial Cortex**
```{r echo=FALSE}
covariates <- data.frame(frontal.medial$glucest.sex, frontal.medial$glucest.age_scan)
pcor.test(frontal.medial$GluCEST_HarvardOxford_Cortical_Reward.Frontal_Medial_Cortex_mean, frontal.medial$glucest.BAS_Reward_totalscore, covariates)
```

**Subcollosal Cortex**
```{r echo=FALSE}
covariates <- data.frame(subcallosal.cortex$glucest.sex, subcallosal.cortex$glucest.age_scan)
pcor.test(subcallosal.cortex$GluCEST_HarvardOxford_Cortical_Reward.Subcallosal_Cortex_mean, subcallosal.cortex$glucest.BAS_Reward_totalscore, covariates)
```

**Paracingulate Gyrus**
```{r echo=FALSE}
covariates <- data.frame(paracingulate$glucest.sex, paracingulate$glucest.age_scan)
pcor.test(paracingulate$GluCEST_HarvardOxford_Cortical_Reward.Paracingulate_Gyrus_mean, paracingulate$glucest.BAS_Reward_totalscore, covariates)
```

**Anterior Cingulate**
```{r echo=FALSE}
covariates <- data.frame(anterior.cingulate$glucest.sex, anterior.cingulate$glucest.age_scan)
pcor.test(anterior.cingulate$GluCEST_HarvardOxford_Cortical_Reward.Anterior_cingulate_mean, anterior.cingulate$glucest.BAS_Reward_totalscore, covariates)
```

**Posterior Cingulate**
```{r echo=FALSE}
covariates <- data.frame(posterior.cingulate$glucest.sex, posterior.cingulate$glucest.age_scan)
pcor.test(posterior.cingulate$GluCEST_HarvardOxford_Cortical_Reward.Posterior_cingulate_mean, posterior.cingulate$glucest.BAS_Reward_totalscore, covariates)
```

\newpage 

## Harvard Oxford Reward Network: Subcortical Regions

**Filter data for reward network subcortical regions, using > 50 mm^3 as region volume threshold for inclusion in analysis**

```{r echo=FALSE}
#get data for the 4 Harvard Oxford subcortical regions reliably present in the GluCEST reward network, and filter out cases that do not meet the minimum coverage requirement ( > 50 mm^3 for each region)

GluCEST_HarvardOxford_SubCortical_Reward <- GluCEST_HarvardOxford_SubCortical_Reward %>% mutate(BrainStem.Midbrain_mean = ((((Brain.Stem_mean)*(Brain.Stem_numvoxels)) + ((Unlabeled_voxels_mean)*(Unlabeled_voxels_numvoxels)))/((Brain.Stem_numvoxels)+(Unlabeled_voxels_numvoxels))))

GluCEST_HarvardOxford_SubCortical_Reward <- GluCEST_HarvardOxford_SubCortical_Reward %>% mutate(BrainStem.Midbrain_numvoxels = ((Brain.Stem_numvoxels)+(Unlabeled_voxels_numvoxels)))

brainstem.midbrain <- data.frame(GluCEST_HarvardOxford_SubCortical_Reward$BrainStem.Midbrain_mean,  GluCEST_HarvardOxford_SubCortical_Reward$BrainStem.Midbrain_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore )
brainstem.midbrain <- filter(brainstem.midbrain, GluCEST_HarvardOxford_SubCortical_Reward.BrainStem.Midbrain_numvoxels > 10 )

thalamus <-  data.frame(GluCEST_HarvardOxford_SubCortical_Reward$Right_Thalamus_mean,  GluCEST_HarvardOxford_SubCortical_Reward$Right_Thalamus_numvoxels, glucest$age_scan, glucest$sex, glucest$BAS_Reward_totalscore)
thalamus <- filter(thalamus, GluCEST_HarvardOxford_SubCortical_Reward.Right_Thalamus_numvoxels > 10 )

caudate <-  data.frame(GluCEST_HarvardOxford_SubCortical_Reward$Right_Caudate_mean,  GluCEST_HarvardOxford_SubCortical_Reward$Right_Caudate_numvoxels,  glucest$age_scan,glucest$sex, glucest$BAS_Reward_totalscore)
caudate <- filter(caudate, GluCEST_HarvardOxford_SubCortical_Reward.Right_Caudate_numvoxels > 10 )

accumbens <-  data.frame(GluCEST_HarvardOxford_SubCortical_Reward$Right_Accumbens_mean,  GluCEST_HarvardOxford_SubCortical_Reward$Right_Accumbens_numvoxels, glucest$age_scan,glucest$sex, glucest$BAS_Reward_totalscore)
accumbens <- filter(accumbens, GluCEST_HarvardOxford_SubCortical_Reward.Right_Accumbens_numvoxels > 10 )
```

**Thalamus**
```{r echo=FALSE}
covariates <- data.frame(thalamus$glucest.sex, thalamus$glucest.age_scan)
pcor.test(thalamus$GluCEST_HarvardOxford_SubCortical_Reward.Right_Thalamus_mean, thalamus$glucest.BAS_Reward_totalscore, covariates)
```

**Caudate**
```{r echo=FALSE}
covariates <- data.frame(caudate$glucest.sex, caudate$glucest.age_scan)
pcor.test(caudate$GluCEST_HarvardOxford_SubCortical_Reward.Right_Caudate_mean, caudate$glucest.BAS_Reward_totalscore, covariates)
```

**Accumbens**
```{r echo=FALSE}
covariates <- data.frame(accumbens$glucest.sex, accumbens$glucest.age_scan)
pcor.test(accumbens$GluCEST_HarvardOxford_SubCortical_Reward.Right_Accumbens_mean, accumbens$glucest.BAS_Reward_totalscore, covariates)
```

**Brainstem and Midbrain**
```{r echo=FALSE}
covariates <- data.frame(brainstem.midbrain$glucest.sex, brainstem.midbrain$glucest.age_scan)
pcor.test(brainstem.midbrain$GluCEST_HarvardOxford_SubCortical_Reward.BrainStem.Midbrain_mean, brainstem.midbrain$glucest.BAS_Reward_totalscore, covariates)
```

\newpage

**Partial R Plot (Supplemental Figure S1)**

```{r echo=TRUE}
reward.HO.results <- data.frame(Region=character(), PartialR=double())
reward.HO.results <- reward.HO.results %>% add_row(Region= "Frontal Medial", PartialR= -0.06)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Frontal Pole", PartialR= 0.11)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Anterior Cingulate", PartialR= 0.11)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Superior Frontal", PartialR= 0.13)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Subcallosal", PartialR= 0.29)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Paracingulate", PartialR= 0.29)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Accumbens", PartialR= 0.29)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Midbrain/Brainstem", PartialR= 0.31)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Thalamus", PartialR= 0.36)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Posterior Cingulate", PartialR= 0.40)
reward.HO.results <- reward.HO.results %>% add_row(Region= "Caudate", PartialR= 0.47)

jpeg("/Users/valeriejill/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/Figures/Images/BASRR_RewardNetworkTotal_HarvardOxford_PartialR.jpg", units="in", width=7.3, height=6.6, res=800)

ggplot(data=reward.HO.results, aes(x=Region, y=PartialR, fill=Region)) + geom_col() + 
  labs(x="") +
  labs(y="\nPartial R\n") +
  ggtitle("\n") +
  theme_minimal()+
  theme(
  axis.title.y=element_text(family="Times",  size=20),
  axis.text.y.left= element_text(family="Times",size=18),
  axis.text.x.bottom = element_text(color="black", , angle = 35, hjust= 1.1, vjust= 1.05, size=15),
  axis.text.x = element_text(color="black"),
  axis.text.y = element_text(color="black"),
  axis.line = element_line(colour = "white"),
  axis.line.x = element_line(colour = "black"),
  axis.line.y = element_line(colour = "black"),
  panel.grid.major.y = element_line(colour = "gray90"),
  panel.grid.major.x = element_line(colour = "white"),
  legend.position = "none") +
  scale_y_continuous(breaks=c(0,0.1,0.2,0.3,0.4,0.5), limits = c(-0.07,.5)) +
  scale_fill_manual(values=c("#7c0082", "#7c0082", "#7c0082", "#7c0082", "#7c0082", "#7c0082", "#ffdb3c", "#ffdb3c","#ffdb3c","#7c0082","#ffdb3c"))
```

### FDR correction
```{r echo=TRUE}
ps <- c("0.5243663","0.4162064","0.6619631","0.0621055","0.05856767","0.4718429","0.03024202","0.01662653","0.07915414","0.2245098","0.04523888") #p-values from pcor.test
fdr.ps <- p.adjust(ps, method="fdr")
fdr.ps
```

