---
title: 'Reward Network GluCEST and RR Statistics: Diagnostic Category ROI Analyses'
author: "Valerie Jill Sydnor"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: yes
    toc_depth: '5'
theme: cerulean
geometry: margin=1.9cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Documents/ResearchProjects/GluCEST_BASRewardResponsivity_Project/OutputMeasures/")
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=65),tidy=TRUE)
library(plyr)
library(dplyr)
library(knitr)
library(ggplot2)
```

\newpage 

```{r include=FALSE}
#read in sample demographics and clinical measures
glucest <- read.csv("../GLUCEST-Clinical-Demographics-Measures-N45.csv", header=TRUE) #csv created by Prepare_Demographics_ClinicalMeasures_Data.Rmd
glucest$Control_Coded <- as.factor(glucest$Control_Coded)

#Read in GluCEST % Contrast Measures for Harvard Oxford Atlas Anatomical ROIs
HO.cortical <- read.csv("./GluCEST-HarvardOxford-Cortical-Measures.csv", header=TRUE, sep ='\t')
HO.cortical <- HO.cortical %>% dplyr::select(-Subject)
HO.subcortical <- read.csv("./GluCEST-HarvardOxford-SubCortical-Measures.csv", header=TRUE, sep ='\t')
HO.subcortical <- HO.subcortical %>% dplyr::select(-Subject)

#Merge data frames
glucest <- cbind(glucest, HO.cortical, HO.subcortical)

#Extract data for TD group only
glucest.TD <- glucest %>% filter(Diagnosis_NC_MDD_Pro_Schiz_Coded == 1)
#Extract data for MDD group only
glucest.MDD <- glucest %>% filter(Diagnosis_NC_MDD_Pro_Schiz_Coded == 2)
#Extract data for Prodomal group only
glucest.PRO <- glucest %>% filter(Diagnosis_NC_MDD_Pro_Schiz_Coded == 3)
#Extract data for PSY group only  
glucest.PSY <- glucest %>% filter(Diagnosis_NC_MDD_Pro_Schiz_Coded == 4)

#TD-MDD Data frame
glucest.TD.MDD <- rbind(glucest.TD, glucest.MDD)

#TD-PRO Data frame
glucest.TD.PRO <- rbind(glucest.TD, glucest.PRO)

#TD-PSY Data frame
glucest.TD.PSY <- rbind(glucest.TD, glucest.PSY)

#PSY-PRO Data frame
glucest.PRO.PSY <- rbind(glucest.PRO, glucest.PSY)
glucest.PRO.PSY$Diagnosis_NC_MDD_Pro_Schiz_Coded <- as.factor(glucest.PRO.PSY$Diagnosis_NC_MDD_Pro_Schiz_Coded)
```

\newpage

# Case-Control Analysis: Typically Developing v. Psychotic Disorder Groups

## Anterior Cingulate

* Z-scores
```{r}
control_mean = mean(glucest.TD$Anterior_cingulate_mean)
control_sd = sd(glucest.TD$Anterior_cingulate_mean)
glucest.TD.PSY$Anterior_cingulate_zscore <- round((glucest.TD.PSY$Anterior_cingulate_mean - control_mean) / (control_sd), digits=2)

glucest.TD.PSY %>% group_by(Control_Coded) %>% summarise_at(vars(Anterior_cingulate_zscore), funs(mean(.)))
```

* ANCOVA
```{r}
summary(aov(Anterior_cingulate_mean ~ age_scan + sex + Control_Coded, data=glucest.TD.PSY))
```


## Thalamus

* Z-scores
```{r}
control_mean = mean(glucest.TD$Right_Thalamus_mean)
control_sd = sd(glucest.TD$Right_Thalamus_mean)
glucest.TD.PSY$Right_Thalamus_zscore <- round((glucest.TD.PSY$Right_Thalamus_mean - control_mean) / (control_sd), digits=2)

glucest.TD.PSY %>% group_by(Control_Coded) %>% summarise_at(vars(Right_Thalamus_zscore), funs(mean(.)))
```

* ANCOVA
```{r}
summary(aov(Right_Thalamus_mean ~ age_scan + sex + Control_Coded, data=glucest.TD.PSY))
```

\newpage

# Case-Control Analysis: Typically Developing v. Depressive Disorders Groups

## Anterior Cingulate

* Z-scores
```{r}
control_mean = mean(glucest.TD$Anterior_cingulate_mean)
control_sd = sd(glucest.TD$Anterior_cingulate_mean)
glucest.TD.MDD$Anterior_cingulate_zscore <- round((glucest.TD.MDD$Anterior_cingulate_mean - control_mean) / (control_sd), digits=2)

glucest.TD.MDD %>% group_by(Control_Coded) %>% summarise_at(vars(Anterior_cingulate_zscore), funs(mean(.))) 
```

* ANCOVA
```{r}
summary(aov(Anterior_cingulate_mean ~ age_scan + sex + Control_Coded, data=glucest.TD.MDD))
```


## Thalamus

* Z-scores
```{r}
control_mean = mean(glucest.TD$Right_Thalamus_mean)
control_sd = sd(glucest.TD$Right_Thalamus_mean)
glucest.TD.MDD$Right_Thalamus_zscore <- round((glucest.TD.MDD$Right_Thalamus_mean - control_mean) / (control_sd), digits=2)

glucest.TD.MDD %>% group_by(Control_Coded) %>% summarise_at(vars(Right_Thalamus_zscore), funs(mean(.)))
```
* ANCOVA
```{r}
summary(aov(Right_Thalamus_mean ~ age_scan + sex + Control_Coded, data=glucest.TD.MDD))
```

\newpage 

# Case-Control Analysis: Typically Developing v. Prodromal Symptoms Groups

## Anterior Cingulate

* Z-scores
```{r}
control_mean = mean(glucest.TD$Anterior_cingulate_mean)
control_sd = sd(glucest.TD$Anterior_cingulate_mean)
glucest.TD.PRO$Anterior_cingulate_zscore <- round((glucest.TD.PRO$Anterior_cingulate_mean - control_mean) / (control_sd), digits=2)

glucest.TD.PRO %>% group_by(Control_Coded) %>% summarise_at(vars(Anterior_cingulate_zscore), funs(mean(.)))
```

* ANCOVA
```{r}
summary(aov(Anterior_cingulate_mean ~ age_scan + sex + Control_Coded, data=glucest.TD.PRO))
```


## Thalamus

* Z-scores
```{r}
control_mean = mean(glucest.TD$Right_Thalamus_mean)
control_sd = sd(glucest.TD$Right_Thalamus_mean)
glucest.TD.PRO$Right_Thalamus_zscore <- round((glucest.TD.PRO$Right_Thalamus_mean - control_mean) / (control_sd), digits=2)

glucest.TD.PRO %>% group_by(Control_Coded) %>% summarise_at(vars(Right_Thalamus_zscore), funs(mean(.)))
```
* ANCOVA
```{r}
summary(aov(Right_Thalamus_mean ~  age_scan + sex + Control_Coded, data=glucest.TD.PRO))
```

# Prodromal Symptoms v. Diagnosed Psychotic Disorder

## Anterior Cingulate

* Group means
```{r}
glucest.PRO.PSY %>% group_by(Diagnosis_NC_MDD_Pro_Schiz_Coded) %>% summarise_at(vars(Anterior_cingulate_mean), funs(mean(.)))
```

## Thalamus

* Group means
```{r}
glucest.PRO.PSY %>% group_by(Diagnosis_NC_MDD_Pro_Schiz_Coded) %>% summarise_at(vars(Right_Thalamus_mean), funs(mean(.)))
```
