---
title: 'Reward Network GluCEST and RR Statistics: Prepare Clinical and Demographic Data'
author: "Valerie Jill Sydnor"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: no
    toc_depth: '5'
theme: cerulean
geometry: margin=1.9cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = './')
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=70),tidy=TRUE)
library(dplyr)
library(knitr)
```

#Clean Clinical Data

**Get RedCap data**
```{r echo=TRUE}
clinical_orig <- read.csv("../../ClinicalMeasures/axis_7t_scales_original.csv",
                          header=TRUE)

#fix bblid for case mislabeled in RedCap
clinical_orig$bblid[clinical_orig$bblid == 93724 ] <- 93274
#remove blank self-report entry for bblid 20180. This entry has no clinical measures in it.
clinical_orig <- clinical_orig %>% filter(admin_time_stamp != c("11/5/18 10:11")) 
#remove proband c (collateral) entry for bblid 96659. We are using proband p (patient) measures. 
clinical_orig <- clinical_orig %>% filter(admin_time_stamp != c("12/7/18 18:15")) 
```

**Remove cases from the clinical spreadsheet that are missing GluCEST data**
```{r}
clinical_orig <- clinical_orig %>% filter (bblid != 20016) #20016: participant never scanned
clinical_orig <- clinical_orig %>% filter (bblid != 20049) #20049: participant never scanned
clinical_orig <- clinical_orig %>% filter (bblid != 99032) #99032: participant never scanned
clinical_orig <- clinical_orig %>% filter (bblid != 20181 ) #20181: participant never scanned
clinical_orig <- clinical_orig %>% filter (bblid != 110586) #110586: participant never scanned
clinical_orig <- clinical_orig %>% filter (bblid != 99637 ) #99637:  GluCEST not acquired
clinical_orig <- clinical_orig %>% filter (bblid != 80289 ) #80289: GluCEST acquisition error
```

**Extract study variables from clinical spreadsheet**
```{r}
clinical_orig <- clinical_orig %>% dplyr::select(bblid, admin_time_stamp, date, admin_event, 
                                          protocol, protocol_numbe, starts_with("bisbas"),
                                          starts_with("prime"), starts_with("pds"),
                                          starts_with("eswan_dep"))
clinical_orig <- clinical_orig %>% dplyr::select(-ends_with("dur"), -(bisbas_comments), -ends_with("_c"))
```

**Extract self-report data and save self-report csv: axis_7T_scales_selfreport.csv**
```{r}
#extract self-report data 
scales_selfreport <- clinical_orig %>% filter(admin_event == "selfr_1")
#save into csv
write.csv(scales_selfreport,file="../../ClinicalMeasures/axis_7T_scales_selfreport.csv", row.names = F)
```

\newpage

#Calculate BAS, PRIME, and PROMIS Scores

###Behavioral Activation Scale
```{r}
#reverse score items
attach(scales_selfreport)
for(num in c("1","3","4","5","6","7","8","9","10","11","12","13",
             "14","15","16","17","18","19","20","21","23","24")){ #items other than 2 and 22 are reversed scored
scalename <- sprintf("bisbas_%s",num)
scalename_rev <- sprintf("bisbas_%s_rev",num)
scaledata <- get(scalename)
scales_selfreport[scalename_rev] = NULL #create new column for reverse scores
scales_selfreport[[scalename_rev]][scaledata == 1] <- 4 #reverse score
scales_selfreport[[scalename_rev]][scaledata == 2] <- 3 #reverse score
scales_selfreport[[scalename_rev]][scaledata == 3] <- 2 #reverse score
scales_selfreport[[scalename_rev]][scaledata == 4] <- 1 #reverse score
}
detach(scales_selfreport)

#BAS Reward Responsiveness: sum items 4,7,14,18,23
scales_selfreport <- scales_selfreport %>% mutate(BAS_Reward_totalscore = bisbas_4_rev +
                        bisbas_7_rev + bisbas_14_rev + bisbas_18_rev + bisbas_23_rev)

#BAS Drive: sum items 3,9,12,21
scales_selfreport <- scales_selfreport %>% mutate(BAS_Drive_totalscore = bisbas_3_rev 
           + bisbas_9_rev + bisbas_12_rev + bisbas_21_rev)

#BAS Fun: sum items 5,10,15,20
scales_selfreport <- scales_selfreport %>% mutate(BAS_Fun_totalscore = bisbas_5_rev 
                + bisbas_10_rev + bisbas_15_rev + bisbas_20_rev)
```

###Prime Screen
```{r}
#impute two missing prime_4 scores by averaging all other prime items
case119791 <- filter(scales_selfreport, bblid == 119791)
case132179 <- filter(scales_selfreport, bblid == 132179)

case119791_imputedprime4 <- ((case119791$prime_1 + case119791$prime_2 + case119791$prime_3 + 
                              case119791$prime_5 + case119791$prime_6 + case119791$prime_7 + 
                              case119791$prime_8 + case119791$prime_9 + case119791$prime_10 + 
                              case119791$prime_11 + case119791$prime_12)/11)
case132179_imputedprime4 <- ((case132179$prime_1 + case132179$prime_2 + case132179$prime_3 + 
                              case132179$prime_5 + case132179$prime_6 + case132179$prime_7 + 
                              case132179$prime_8 + case132179$prime_9 + case132179$prime_10 + 
                              case132179$prime_11 + case132179$prime_12)/11)

scales_selfreport[45,35] <- round(case119791_imputedprime4)
scales_selfreport[51,35] <- round(case132179_imputedprime4)

#PRIME Total Score: sum all 12 items
scales_selfreport <- scales_selfreport %>% mutate(Prime_totalscore = prime_1 + prime_2 + prime_3 
     + prime_4 + prime_5 + prime_6 + prime_7 + prime_8 + prime_9 + prime_10 + prime_11 + prime_12) 
```

###Promis Depression Scale
```{r}
#PROMIS Total Score: sum all 8 items
scales_selfreport <- scales_selfreport %>% mutate(PROMIS_totalscore = pds_1 + pds_2 + pds_3 + pds_4 
                                                  + pds_5 + pds_6 + pds_7 + pds_8)
```

**Save self-report summary scores csv: 7TClinical_SummaryMeasures.csv**
```{r}
write.csv(scales_selfreport,file="../../ClinicalMeasures/7TClinical_Summarymeasures.csv", row.names = F)
```

\newpage

#Clean Demographics Data

**Read in demographics and visual quality assurance results**
```{r}
glucest_demographics <- read.csv("../../DemographicMeasures/GluCEST-Demographics.csv", header=TRUE)
```

**Identify study sample: identify all baseline (timepoint 1) cases that have GluCEST data and RedCap data, and that additionally passed all Quality Assurance checks**
```{r}
#filter by cases with timepoint=1 and PassQC=1 (i.e., remove follow up scans and cases that failed QA)
glucest_tmpt1_passQC_demographics <- glucest_demographics %>% 
                                    filter(Timepoint == "1" & FinalCEST_PassQC == "1")
#remove case missing all clinical data
glucest_tmpt1_passQC_demographics <- glucest_tmpt1_passQC_demographics %>% filter(Case != "112126_11157")
#rename record_id to bblid
glucest_tmpt1_passQC_demographics <- glucest_tmpt1_passQC_demographics %>% rename(bblid= record_id)
```

**Write final caselist/bblid list and save demographics csv: GluCEST_Demographics_Timept1_PassQC.csv**
```{r}
#save final demographics csv with timepoint 1 Pass QA cases (N=45, final study sample)
write.csv(glucest_tmpt1_passQC_demographics,
          file="../../DemographicMeasures/GluCEST_Demographics_Timept1_PassQC.csv", row.names = F)
#save the final study caselist 
timpt1_passQC_caselist <- data.frame(glucest_tmpt1_passQC_demographics$Case)
write.table(timpt1_passQC_caselist, file="./SCANID-Timepoint1-PassQC.csv", sep=",", 
            col.names=FALSE, row.names=FALSE, quote=FALSE)
#save the final bblid list
timpt1_passQC_bblid <- data.frame(glucest_tmpt1_passQC_demographics$bblid)
write.table(timpt1_passQC_bblid, file="./BBLID-Timepoint1-PassQC.csv", 
            sep=",", col.names=FALSE, row.names=FALSE, quote=FALSE)
```

\newpage 

#Create Study-Specific Clinical & Demographics Spreadsheet

**Extract self-report clinical measures for final study sample (N=45)**
```{r}
system("./extract_sample_7TClinicalMeasures.sh", wait=TRUE) #bash script
```

**Read in final study sample clinical measures and demographics**
```{r}
#Demographics Data
demographics_final <- read.csv("../../DemographicMeasures/GluCEST_Demographics_Timept1_PassQC.csv", 
                               header = TRUE)
#Clinical Data
clinical_final <- read.csv("../../ClinicalMeasures/7TClinical_Summarymeasures_Timept1_PassQC.csv",
                           header=TRUE)
```

**Save final demographics/clinical measures csv: GLUCEST-Clinical-Demographics-Measures-N45.csv**
```{r}
GLUCEST_DATA <- Reduce(function(x, y) merge(x, y, all=TRUE, sort=FALSE),
                list(demographics_final, clinical_final))

write.csv(GLUCEST_DATA, file="../../GLUCEST-Clinical-Demographics-Measures-N45.csv", row.names=F)
```
