---
title: 'Reward Network GluCEST and RR Statistics: Sample Characteristics'
author: "Valerie Jill Sydnor"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: yes
    toc_depth: '5'
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
theme: cerulean
geometry: margin=1.9cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = './')
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=70),tidy=TRUE)
library(dplyr)
library(knitr)
library(kableExtra)
```

\  

**Table 1**
```{r, echo=F}
#Table 1 inputs
Demotable <- data.frame(Variable=character(),Study_Sample=double(), Typically_Developing=double(), Clinical=double(), Pvalue=character())
Demotable <- Demotable %>% add_row(Variable = "Age", Study_Sample= 22.7, Typically_Developing= 22.6, Clinical= 22.9, Pvalue=as.character("n.s."))
Demotable <- Demotable %>% add_row(Variable = "Sex (M)", Study_Sample = 15, Typically_Developing= 5 , Clinical= 10,  Pvalue="n.s.")
Demotable <- Demotable %>% add_row(Variable = "BAS RR", Study_Sample = 17.4, Typically_Developing= 17.5, Clinical= 17.3,  Pvalue="n.s.")
Demotable <- Demotable %>% add_row(Variable = "PROMIS", Study_Sample = 12.8, Typically_Developing= 9.7, Clinical= 14.4, Pvalue="0.0017")
Demotable <- Demotable %>% add_row(Variable = "Prime", Study_Sample = 6.0, Typically_Developing= 0.5, Clinical= 8.7, Pvalue="0.0003")

Demotable %>%
  kable() %>%
  kable_styling()
```

\newpage
```{r echo=TRUE}
#Read in sample demographics and clinical measures
glucest <- read.csv("../../GLUCEST-Clinical-Demographics-Measures-N45.csv", header=TRUE) #csv created by Prepare_Demographics_ClinicalMeasures_Data.Rmd
```

#Sample Demographics and Clinical Characteristics (Table 1)

##Study Sample (N=45)

**Age**

* Age Mean
```{r}
mean(glucest$age_scan)
```
* Age SD
```{r}
sd(glucest$age_scan)
```

**Sex**

* Number Females
```{r}
length(which(glucest$sex == "2"))
```
* Number Males
```{r}
length(which(glucest$sex == "1"))
```

**Race**

```{r}
sample_race1_count <-  length(which(glucest$race == "1"))
sample_race2_count <-  length(which(glucest$race == "2"))
sample_race4_count <-  length(which(glucest$race == "4"))
sample_race5_count <-  length(which(glucest$race == "5"))
table(glucest$race)
```

**BAS Reward Responsiveness Score**

* BAS RR Score Mean
```{r}
mean(glucest$BAS_Reward_totalscore)
```
* BAS RR Score SD
```{r}
sd(glucest$BAS_Reward_totalscore)
``` 

**PROMIS Score**

* PROMIS Score Mean
```{r}
mean(glucest$PROMIS_totalscore)
```
* PROMIS Score SD
```{r}
sd(glucest$PROMIS_totalscore)
```

**PRIME Score**

* PRIME Score Mean
```{r}
mean(glucest$Prime_totalscore)
```
* PRIME Score SD
```{r}
sd(glucest$Prime_totalscore)
```

\newpage

##Typically Developing (N=15)
```{r}
TD <- filter(glucest, Control_Coded == "1")
```

**Age**

* Age Mean
```{r}
mean(TD$age_scan)
```
* Age SD
```{r}
sd(TD$age_scan)
```

**Sex**

* Number Females
```{r}
length(which(TD$sex == "2"))
```
* Number Males
```{r}
length(which(TD$sex == "1"))
```

**Race**

```{r}
sample_race1_count <-  length(which(TD$race == "1"))
sample_race2_count <-  length(which(TD$race == "2"))
sample_race4_count <-  length(which(TD$race == "4"))
sample_race5_count <-  length(which(TD$race == "5"))
table(TD$race)
```

**BAS Reward Responsiveness Score**

* BAS RR Score Mean
```{r}
mean(TD$BAS_Reward_totalscore)
```
* BAS RR Score SD
```{r}
sd(TD$BAS_Reward_totalscore)
``` 

**PROMIS Score**

* PROMIS Score Mean
```{r}
mean(TD$PROMIS_totalscore)
```
* PROMIS Score SD
```{r}
sd(TD$PROMIS_totalscore)

```

**PRIME Score**

* PRIME Score Mean
```{r}
mean(TD$Prime_totalscore)
```
* PRIME Score SD
```{r}
sd(TD$Prime_totalscore)
```

\newpage

##Clinical (N=30)
```{r}
clinical <- filter(glucest, Control_Coded == "0")
```

**Age**

* Age Mean
```{r}
mean(clinical$age_scan)
```
* Age SD
```{r}
sd(clinical$age_scan)
```

**Sex**

* Number Females
```{r}
length(which(clinical$sex == "2"))
```
* Number Males
```{r}
length(which(clinical$sex == "1"))
```

**Race**

```{r}
sample_race1_count <-  length(which(clinical$race == "1"))
sample_race2_count <-  length(which(clinical$race == "2"))
sample_race4_count <-  length(which(clinical$race == "4"))
sample_race5_count <-  length(which(clinical$race == "5"))
table(clinical$race)
```

**BAS Reward Responsiveness Score**

* BAS RR Score Mean
```{r}
mean(clinical$BAS_Reward_totalscore)
```
* BAS RR Score SD
```{r}
sd(clinical$BAS_Reward_totalscore)
``` 

**PROMIS Score**

* PROMIS Score Mean
```{r}
mean(clinical$PROMIS_totalscore)
```
* PROMIS Score SD
```{r}
sd(clinical$PROMIS_totalscore)
```

**PRIME Score**

* PRIME Score Mean
```{r}
mean(clinical$Prime_totalscore)
```
* PRIME Score SD
```{r}
sd(clinical$Prime_totalscore)
```

\newpage

#Typically Developing v. Clinical Group Statistics (Table 1)

##Age
```{r}
age.F.test <- var.test(TD$age_scan, clinical$age_scan) #F=1.0611, p=0.8558
t.test(glucest$age_scan ~ glucest$Control_Coded, var.equal=TRUE)
```

##Sex
```{r}
chisq.test(glucest$sex, glucest$Control_Coded)
```

##Race
```{r, warning=FALSE}
glucest$race <- as.factor(glucest$race)
chisq.test(glucest$race, glucest$Control_Coded)
```

##BAS Reward Responsiveness Score
```{r}
BASRR.F.test <- var.test(TD$BAS_Reward_totalscore, clinical$BAS_Reward_totalscore) #F=0.412, p=0.0868
t.test(glucest$BAS_Reward_totalscore ~ glucest$Control_Coded, var.equal=TRUE)
```

##PROMIS Depression Score
```{r}
PROMIS.F.test <- var.test(TD$PROMIS_totalscore, clinical$PROMIS_totalscore) #F=0.0668, p=3.812e-06
t.test(glucest$PROMIS_totalscore ~ glucest$Control_Coded, var.equal=FALSE)
```

##PRIME Score
```{r}
PRIME.F.test <- var.test(TD$Prime_totalscore, clinical$Prime_totalscore) #F=0.0101, p=1.255e-11
t.test(glucest$Prime_totalscore ~ glucest$Control_Coded, var.equal=FALSE)
```

\newpage

#BAS Reward Responsiveness Score in Males v. Females

**Entire Sample**
```{r}
BASRR.F.test.sex <- var.test(glucest$BAS_Reward_totalscore ~ glucest$sex) #F=0.578, p=0.2797
t.test(glucest$BAS_Reward_totalscore ~ glucest$sex, var.equal=TRUE)
```
